StarCraft Bots and Competitions

### 2015-12-16 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
read the paper beginning to end fixing typos, updating URLs (google code urls were old), and adding a quick and dirty conclusions section

Thanks to the recent organization of international game AI competitions focused around the popular StarCraft game (see Section \ref{sec:competition}), several groups have been working on integrating many of the techniques described in the previous section into complete ``bots'', capable of playing complete StarCraft games. In this section we will overview some of the currently available top bots.

@@

Playing an RTS game involves dealing with all the problems described above. A few approaches, like CAT \cite{LTW}, Darmok \cite{OntanonMSR10} or ALisp \cite{Marthi05} try to deal with the problem in a monolithic manner, by using a single AI technique. However, none of those systems aims at achieving near human performance. In order to achieve human-level performance, RTS AI designers use a lot of domain knowledge in order to divide the task of playing the game into a collection of sub-problems, which can be dealt-with using individual AI techniques.

@@

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  {\em combat}, and  divide-and-conquer for
  {\em economy}  and  {\em intelligence  gathering}. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for {\em combat},
  and  divide-and-conquer for  {\em economy}.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://github.com/davechurchill/ualbertabot/}}:
  also  uses abstraction  in  {\em combat} like  the previous  two
  bots. But it  also uses it in {\em economy}: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  We  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{http://code.google.com/p/aiurproject/}}:  is
  mainly divide-and-conquer oriented,
  with a  slight abstraction on  {\em economy} due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. {\em Combat} is divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the  current mood. This bot  does not manage however  any kind of
  reactive controls so far.
\item  BTHAI\footnote{\url{http://code.google.com/p/bthai/}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}

@@

In conclusion, we can see that there are two basic tools that can be used in an integration architecture: abstraction and divide-and-conquer, which are widely used by the existing StarCraft bots. For space reasons, we do not include an exhaustive comparison of the architectures of all the participating bots. Some other bots have been documented by their authors, such as SCAIL \cite{YoungSCAIL} or QUORUM \cite{young2012evolutionary}.
%This section has focused on discussing the architecture of existing StarCraft bots. 
Let us now focus on their performance.

@@

This section reviews the results of three recent international competitions on AI for StarCraft. These competitions
%, typically co-located with scientific conferences, 
have been possible thanks to the existence of the Brood War Application Programming Interface 
(BWAPI)\footnote{\url{http://code.google.com/p/bwapi/}}, which 
enables replacing the human player interface with C++ code.
%A consequence of this indirect way of integrating new bots is that every machine can only run one custom bot, requiring two computers for a 2-player game.
The following subsections summarize the results of StarCraft AI competitions co-located with two scientific conferences -- AIIDE (Artificial Intelligence for Interactive Digital Entertainment) and CIG (Computational Intelligence in Games) -- and one stand\-alone competition called SSCAIT (Student StarCraft AI Tournament), during the past years. Since 2011, the CIG and AIIDE competitions have typically been held in August / September in each year, as the conferences are scheduled quite close to each other, and SSCAIT have been held in December / January. As a consequence of this, AIIDE and CIG competitions share a big portion of the entrants.

@@

\subsubsection{AIIDE 2010}

@@

\subsubsection{AIIDE 2011}

@@

\subsubsection{AIIDE 2012}

@@

\subsubsection{AIIDE 2013}

@@

\subsubsection{AIIDE 2014}

@@

\subsubsection{AIIDE 2015}

The 2015 AIIDE competition was the largest competition to date with 23 total bots competing. The competition environment was also changed so that the tournament was now run on virtual machines instea dof physical machines. Doing this enabled the tournament to run for a full two weeks instead of the normal one week, resulting in a total of 20788 games being played - 90 full round robins between each bot pairing. 2015 saw the most even distribution of race selection ever in a Starcraft AI competition, with 5 new Zerg submissions along with 7 Protoss bots and 9 Terran bots. The first ever Random race entry was also submitted as UAlbertaBot had been updated to play all three of the available races. When playing Random race, Starcraft randomly assigns one of Protoss, Terran, or Zerg after the game has started, with your opponent not knowing which race you are until they have scouted you on the map. This provides a significant advantage as the enemy's initial build order must now have a period of uncertainty during which is has to guess what race it is playing against.

@@

\subsubsection{CIG 2011}

@@

\subsubsection{CIG 2012}

@@

\subsubsection{CIG 2013} The CIG 2013 competition was once again
organized by Mike Preuss (TU Dortmund) and Tobias Mahlmann (ITU Copenhagen),
adding Antonio Mora Garc{\'i}a from the Universidad de Granada as
third team member. Whereas the rules and even the participants
to this competition were almost identical to the AIIDE 2013
competition setup, several technical changes were made in comparison
to 2012\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/StarCraft-cig2013}}.
A new competition software was implemented by Tobias but
not completely finished in time, so that the read/write function
that enables learning between games had to be disabled again. 
This is probably the most important difference to the AIIDE competition,
however, as the result provided in table~\ref{tab:cig2013} shows, the effect is
limited. Due to the late availability of the competition software,
only 32 rounds of random robin were played, making 896 games
altogether, and 224 games by each of the 8 submitted bots.

@@

\subsubsection{CIG 2014}
The CIG 2014 competition was organized by Kyung-Joong Kim, Ho-Chul Cho, and In-Seok Oh of Sejong University. For 2014, the CIG competition used a total of 20 different maps which were unknown to the competitors before the competition started, which was by far the most maps ever used in a Starcraft AI competition and presented a challenge to many of the bots who entered. A total of 4680 games were played which meant that each bot played each other bot 60 times, or 3 times per map. The CIG 2014 competition was held just a few weeks before the AIIDE 2014 competition and so many of the entrants to the competition were identical, and the results definitely showed this. The top 4 bots were all the same as the 2014 AIIDE competition with IceBot coming 1st, Ximp in 2nd, LetaBot in 3rd and Aiur in 4th place. For descriptions of these bots please refer to the AIIDE 2014 competition description as none of the top-finishing bots had any significant changes made.

@@

\subsubsection{CIG 2015}
There were some significant rule changes to the CIG 2015 competition, which was once organized by mebers from Sejong University. The most significant rule change was that entrants no longer had to be open source, in an attempt to attract more competitors who may not want to open source their bots. The second rule change was that a single competitor could submit multiple entries to the competition - which caused some controversy among registrants since this introduces the possibility of collusion between entries. Thankfully no such collusion was detected during the competition. The 2015 competition was also not run quite as long as previous competitions with only 2730 games being played in total, or 30 between each bot pairing, 6 between each bot on each of the 5 chosen maps. There were several new Zerg entries to the CIG 2015 competition which ended up finishing in the top three positions, with results very similar to those of the AIIDE 2015 competition. ZZZBot took 1st place, tscmoo-Z (a Zerg bot written by tscmoo) came 2nd, and Overkill came 3rd. For descriptions of these bots and their strategies used please refer to the AIIDE 2015 competition section as the strategies remained largely unchanged between the CIG and AIIDE competitions.

@@

\subsubsection{SSCAIT 2011}
Taking place in winter of 2011, the first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

The first year of SSCAIT hosted 50 participants, all of whom were students of Comenius University at the time. The participants were allowed to select any race and use all the units and technologies in complete 1 vs. 1 games of StarCraft. Vast majority of the bots were implemented to execute hard-coded strategies and behaviour. Participants were divided into 10 groups of 5 people, and 16 of them advanced into a double elimination bracket. Final match of the elimination bracket was won by R. Danielis with a 2-1 score against M. Piovar\v{c}i (both playing as Zerg).

@@

\subsubsection{SSCAIT 2012-2015}
In 2012, the SSCAIT became a truly international competition with 52 participants from numerous universities including 
UC Berkeley (USA), University of Alberta (CAN), Washington State University (USA), University of Nantes (FRA), University of Grenoble (FRA), New University of Lisbon (POT), Gdansk University of Technology (POL), Ritsumeikan University (JAP), University of Bielefeld (GER), Sofia University (BUL), Comenius University (SVK), University of \v{Z}ilina (SVK) and Technical University in Ko\v{s}ice (SVK), as well as a number of non-student participants.

@@

\textbf{{Sandbox phase}} is played non-stop during first 11 months of the year. All the games are streamed via a video streaming service, such as Twitch.tv or Hitbox.tv. The stream is meant to attract new entrants and to help current participants improve their bots before the second phase begins. The participants can watch their bots play against randomly selected other bots. They are allowed to upload new versions of the bots via a web interface at any time during this phase. The  sandbox phase has no winners. However, the bots may use this long phase to collect useful data about their opponent's behaviour.

@@

The results of SSCAIT seasons 2012-2015 follow:
\begin{itemize}
  \item {\bf 2012:} 52 participants. Student division winners: 
  	\begin{enumerate}
  	  \item Matej Isten\'{i}k's bot
  	  \item Marcin Bartnicki's bot
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: ICEBot, after defeating Marcin Bartnicki's bot. 
  \item {\bf 2013:} 50 participants. Student division winner after 1190 round-robin games: 
    \begin{enumerate}
  	  \item Ximp
  	  \item W.O.P.R.
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: Krasi0, after defeating ICEBot.
  \item {\bf 2014:} 42 participants. Student division winner after 861 round-robin games: 
    \begin{enumerate}
  	  \item LetaBot
  	  \item W.O.P.R.
  	  \item UAlbertaBot, with the same win rate as W.O.P.R., but with a loss in a mutual game
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: LetaBot, after defeating Ximp.
  \item {\bf 2015:} At the time of writing this, the SSCAIT 2015 is still in a sandbox phase. 45 bots have registered for the competitive phase so far, including two bots playing as ``Random'' race. The season will be concluded by an elimination bracket featuring 16 bots in 2015.
\end{itemize}

@@

>>>>

Thanks to the recent organization of international game AI competitions focused around the popular StarCraft game, several groups have been working on integrating many of the techniques developed for RTS game AI into complete ``bots'', capable of playing complete StarCraft games. In this chapter we will overview some of the currently available top bots, and their results of recent competitions.

@@

Playing an RTS game involves dealing with a wide variety of problems, ranging from miro-management problems such as unit control, to macro-management problems such as resource allocation. A few approaches, like CAT \cite{LTW}, Darmok \cite{OntanonMSR10} or ALisp \cite{Marthi05} try to deal with the problem in a monolithic manner, by using a single AI technique. However, none of those systems aims at achieving near human performance. In order to achieve human-level performance, RTS AI designers use a lot of domain knowledge in order to divide the task of playing the game into a collection of sub-problems, which can be dealt-with using individual AI techniques.

@@

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  {\em combat}, and  divide-and-conquer for
  {\em economy}  and  {\em intelligence  gathering}. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for {\em combat},
  and  divide-and-conquer for  {\em economy}.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://github.com/davechurchill/ualbertabot/}}:
  also  uses abstraction  in  {\em combat} like  the previous  two
  bots. But it  also uses it in {\em economy}: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  We  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{https://github.com/AIUR-group/AIUR}}:  is
  mainly divide-and-conquer oriented,
  with a  slight abstraction on  {\em economy} due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. {\em Combat} is divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the  current mood. This bot  does not manage however  any kind of
  reactive controls so far.
\item  BTHAI\footnote{\url{https://github.com/jhagelback/opprimobot}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}

@@

In conclusion, we can see that there are two basic tools that can be used in an integration architecture: abstraction and divide-and-conquer, which are widely used by the existing StarCraft bots. For space reasons, we do not include an exhaustive comparison of the architectures of all the participating bots. Some more bots than the ones described here have been documented by their authors, such as SCAIL \cite{YoungSCAIL} or QUORUM \cite{young2012evolutionary}.
%This section has focused on discussing the architecture of existing StarCraft bots. 
Let us now focus on their performance in recent competitions.

@@

This section reviews the results of three recent international competitions on AI for StarCraft. These competitions
%, typically co-located with scientific conferences, 
have been possible thanks to the existence of the Brood War Application Programming Interface 
(BWAPI)\footnote{\url{https://github.com/bwapi/bwapi}}, which 
enables replacing the human player interface with C++ code.
%A consequence of this indirect way of integrating new bots is that every machine can only run one custom bot, requiring two computers for a 2-player game.
The following subsections summarize the results of StarCraft AI competitions co-located with two scientific conferences -- AIIDE (Artificial Intelligence for Interactive Digital Entertainment) and CIG (Computational Intelligence in Games) -- and one stand\-alone competition called SSCAIT (Student StarCraft AI Tournament), during the past years. Since 2011, the CIG and AIIDE competitions have typically been held in August / September in each year, as the conferences are scheduled quite close to each other, and SSCAIT have been held in December / January. As a consequence of this, AIIDE and CIG competitions share a big portion of the entrants.

@@

\subsubsection{AIIDE 2010.}

@@

\subsubsection{AIIDE 2011.}

@@

\subsubsection{AIIDE 2012.}

@@

\subsubsection{AIIDE 2013.}

@@

\subsubsection{AIIDE 2014.}

@@

\subsubsection{AIIDE 2015.}

The 2015 AIIDE competition was the largest competition to date with 23 total bots competing. The competition environment was also changed so that the tournament was now run on virtual machines instead of physical machines. Doing this enabled the tournament to run for a full two weeks instead of the normal one week, resulting in a total of 20788 games being played - 90 full round robins between each bot pairing. 2015 saw the most even distribution of race selection ever in a Starcraft AI competition, with 5 new Zerg submissions along with 7 Protoss bots and 9 Terran bots. The first ever Random race entry was also submitted as UAlbertaBot had been updated to play all three of the available races. When playing Random race, Starcraft randomly assigns one of Protoss, Terran, or Zerg after the game has started, with your opponent not knowing which race you are until they have scouted you on the map. This provides a significant advantage as the enemy's initial build order must now have a period of uncertainty during which is has to guess what race it is playing against.

@@

\subsubsection{CIG 2011.}

@@

\subsubsection{CIG 2012.}

@@

\subsubsection{CIG 2013.} The CIG 2013 competition was once again
organized by Mike Preuss (TU Dortmund) and Tobias Mahlmann (ITU Copenhagen),
adding Antonio Mora Garc{\'i}a from the Universidad de Granada as
third team member. Whereas the rules and even the participants
to this competition were almost identical to the AIIDE 2013
competition setup, several technical changes were made in comparison
to 2012\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/StarCraft-cig2013}}.
A new competition software was implemented by Tobias but
not completely finished in time, so that the read/write function
that enables learning between games had to be disabled again. 
This is probably the most important difference to the AIIDE competition,
however, as the result provided in table~\ref{tab:cig2013} shows, the effect is
limited. Due to the late availability of the competition software,
only 32 rounds of random robin were played, making 896 games
altogether, and 224 games by each of the 8 submitted bots.

@@

\subsubsection{CIG 2014.}
The CIG 2014 competition was organized by Kyung-Joong Kim, Ho-Chul Cho, and In-Seok Oh of Sejong University. For 2014, the CIG competition used a total of 20 different maps which were unknown to the competitors before the competition started, which was by far the most maps ever used in a Starcraft AI competition and presented a challenge to many of the bots who entered. A total of 4680 games were played which meant that each bot played each other bot 60 times, or 3 times per map. The CIG 2014 competition was held just a few weeks before the AIIDE 2014 competition and so many of the entrants to the competition were identical, and the results definitely showed this. The top 4 bots were all the same as the 2014 AIIDE competition with IceBot coming 1st, Ximp in 2nd, LetaBot in 3rd and Aiur in 4th place. For descriptions of these bots please refer to the AIIDE 2014 competition description as none of the top-finishing bots had any significant changes made.

@@

\subsubsection{CIG 2015.}
There were some significant rule changes to the CIG 2015 competition, which was once organized by mebers from Sejong University. The most significant rule change was that entrants no longer had to be open source, in an attempt to attract more competitors who may not want to open source their bots. The second rule change was that a single competitor could submit multiple entries to the competition - which caused some controversy among registrants since this introduces the possibility of collusion between entries. Thankfully no such collusion was detected during the competition. The 2015 competition was also not run quite as long as previous competitions with only 2730 games being played in total, or 30 between each bot pairing, 6 between each bot on each of the 5 chosen maps. There were several new Zerg entries to the CIG 2015 competition which ended up finishing in the top three positions, with results very similar to those of the AIIDE 2015 competition. ZZZBot took 1st place, tscmoo-Z (a Zerg bot written by tscmoo) came 2nd, and Overkill came 3rd. For descriptions of these bots and their strategies used please refer to the AIIDE 2015 competition section as the strategies remained largely unchanged between the CIG and AIIDE competitions.

@@

\subsubsection{SSCAIT 2011.}
Taking place in winter of 2011, the first SSCAIT tournament was organized by Michal \v{C}ertick\'{y} as part of the {\em ``Introduction to Artificial Intelligence''} course at the Department of Applied Informatics, Comenius University in Bratislava, Slovakia. It was inspired by the media coverage of AIIDE StarCraft AI competition held in 2010, but over the following years it diverged from AIIDE competition's format significantly.

The first year of SSCAIT hosted 50 participants, all of whom were students of Comenius University at the time. The participants were allowed to select any race and use all the units and technologies in complete 1 vs. 1 games of StarCraft. Vast majority of the bots were implemented to execute hard-coded strategies and behavior. Participants were divided into 10 groups of 5 people, and 16 of them advanced into a double elimination bracket. Final match of the elimination bracket was won by R. Danielis with a 2-1 score against M. Piovar\v{c}i (both playing as Zerg).

@@

\subsubsection{SSCAIT 2012-2015.}
In 2012, the SSCAIT became a truly international competition with 52 participants from numerous universities including 
UC Berkeley (USA), University of Alberta (CAN), Washington State University (USA), University of Nantes (FRA), University of Grenoble (FRA), New University of Lisbon (POT), Gdansk University of Technology (POL), Ritsumeikan University (JAP), University of Bielefeld (GER), Sofia University (BUL), Comenius University (SVK), University of \v{Z}ilina (SVK) and Technical University in Ko\v{s}ice (SVK), as well as a number of non-student participants.

@@

\textbf{{Sandbox phase}} is played non-stop during first 11 months of the year. All the games are streamed via a video streaming service, such as Twitch.tv or Hitbox.tv. The stream is meant to attract new entrants and to help current participants improve their bots before the second phase begins. The participants can watch their bots play against randomly selected other bots. They are allowed to upload new versions of the bots via a web interface at any time during this phase. The  sandbox phase has no winners. However, the bots may use this long phase to collect useful data about their opponent's behavior.

@@

The results of SSCAIT seasons 2012-2015 follow:
\begin{itemize}
  \item {\bf 2012:} 52 participants. Student division winners: 
  	\begin{enumerate}
  	  \item Matej Isten\'{i}k's bot
  	  \item Marcin Bartnicki's bot
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: ICEBot, after defeating Marcin Bartnicki's bot. 
  \item {\bf 2013:} 50 participants. Student division winner after 1190 round-robin games: 
    \begin{enumerate}
  	  \item Ximp
  	  \item W.O.P.R.
  	  \item UAlbertaBot
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: Krasi0, after defeating ICEBot.
  \item {\bf 2014:} 42 participants. Student division winner after 861 round-robin games: 
    \begin{enumerate}
  	  \item LetaBot
  	  \item W.O.P.R.
  	  \item UAlbertaBot, with the same win rate as W.O.P.R., but with a loss in a mutual game.
  	\end{enumerate}
  Mixed division winner of the elimination bracket of 8 bots: LetaBot, after defeating Ximp.
  \item {\bf 2015:} At the time of writing this, the SSCAIT 2015 is still in a sandbox phase. 45 bots have registered for the competitive phase so far, including two bots playing as ``Random'' race. The season will be concluded by an elimination bracket featuring 16 bots in 2015.
\end{itemize}

@@

\section{Conclusions}

Competitions have historically been an important drive in artificial intelligence, with challenge tasks such as {\em Chess}, {\em Go}, autonomous vehicle driving, among others having resulted in many algorithmic and theoretical breakthroughs. For that reason, we believe RTS AI competitions are playing and will continue to play an important role in the field by both motivating new research and also being an incentive to attract new students and researchers to work on some of the key open challenges of RTS AI.

This chapter has provided a summary of the results of the most three most important StarCraft AI competitions, organized during the past six years, as well as a summary of the architectures used by some of the bots that regularly participate in these competitions. Moreover, as evidenced by the poor results that the top bots in these competitions achieve when playing against good human players, a significant amount of open questions remain about how to design AI systems that can handle real-time adversarial domains such as StarCraft. Hopefully, these competitions can play an important role in motivating research programs that can ultimately answer these questions.
